Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2018-11-05 papers/paper/paper.tex
Move figures around and remove onebound-vs-steplen hist

\begin{figure}[tbhp]
  \centering
  a)\includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
  b)\includegraphics[width=\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
  c)\includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
  \caption{\davidsays{Look up Yildiz figure for (a)}\textbf{Does our model capture dynamics a markov model wouldn't?}}
\label{fig:}
\end{figure}

>>>>

\begin{figure}[tbhp]
  \includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
  \includegraphics[width=\linewidth]{../../plots/paper_unbinding_probability_vs_displacement.pdf}
  \caption{\textbf{Tension gating of model} \davidsays{Look up Yildiz figure}}
  \label{fig:tensiongating}
\end{figure}

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
  \caption{\textbf{Does our model capture dynamics a markov model wouldn't?}}
\label{fig:}
\end{figure}
